\begin{adjustwidth}{0.2cm}{0.2cm}

    % supervisor statement
    \begin{center}
        {\englishfont\fontsize{14pt}{21pt}\selectfont \textbf{ACKNOWLEDGMENTS} \par}
    \end{center}
    \label{acknowledgements}

    \vspace{1cm}
    \setlength{\parindent}{2em}
    {\large I would like to express my gratitude to my supervisor, Mr. Sokchea Kor, for his guidance and expertise. His feedback and support throughout the research process have been instrumental in shaping this work. This research was inspired by Dr. Rina Buoy's contributions to the field. I appreciate the Royal University of Phnom Penh management for establishing this program within the Faculty of Engineering. I would also like to acknowledge khsearch.com, Chuon-Nath Dictionary, Alpha-Word, Google-Word, and Hugging Face for providing essential datasets.\par}

    \vspace{0.5cm}
    {\large I am profoundly thankful to the entire Faculty of Engineering community for their exceptional support and contributions to my academic journey. The knowledge, resources, and supportive environment they provided have been crucial to my success. The faculty's unwavering commitment to excellence and their dedication to nurturing future engineers have created an atmosphere that truly fosters innovation and learning. The state-of-the-art facilities and cutting-edge technology available have enabled me to conduct advanced research in optical character recognition with unprecedented precision. The collaborative spirit among faculty members, researchers, and students has fostered an environment of intellectual growth and continuous innovation. Through numerous workshops, seminars, and technical discussions, I have gained deep insights into the field of computer vision and machine learning. The faculty's strong industry connections and emphasis on practical applications have ensured that my research remains relevant and impactful. Their guidance in implementing transformer-based architectures and synthetic data generation techniques has been particularly valuable. The mentorship provided by senior researchers and the opportunity to participate in various research projects have significantly enhanced my technical capabilities and research methodology.\par}

    \vspace{0.5cm}
    {\large Finally, I would like to thank my friends for their encouragement throughout my studies. Their support and belief in my capabilities have helped make this journey meaningful.\par}

\end{adjustwidth}