\chapter{Experiments}
\phantomsection
\label{ch:experiments}

\section{Experimental Environment and Tools}
\label{sec:environment}
This section describes the hardware, software, and tools used to conduct the OCR experiments.

\section{Model Architecture and Configuration}
\label{sec:architecture}
Details of the model architectures and configurations used in the OCR system.

\subsection{CRAFT for Text Detection}
\label{subsec:craft}
Description of the CRAFT model architecture and its configuration for Khmer text detection.

\subsection{TrOCR for Text Recognition}
\label{subsec:trocr}
Details of the TrOCR transformer-based model used for Khmer text recognition.

\section{Training Methodology}
\label{sec:training}
The training approach and methodology used to develop the OCR models.

\subsection{Fine-tuning CRAFT on Annotated Images}
\label{subsec:craft-training}
Process and parameters for fine-tuning the CRAFT model on annotated Khmer document images.

\subsection{Fine-tuning TrOCR on Synthetic Dataset}
\label{subsec:trocr-training}
Details of fine-tuning TrOCR using the synthetic Khmer dataset.

\section{Evaluation Metrics}
\label{sec:metrics}
Metrics used to evaluate the performance of the OCR system.

\subsection{Detection Metrics (Precision, Recall)}
\label{subsec:detection-metrics}
Text detection evaluation using precision and recall metrics.

\subsection{Recognition Metrics (Accuracy, CER, WER)}
\label{subsec:recognition-metrics}
Text recognition evaluation using character error rate, word error rate, and accuracy metrics.

\section{Baseline and Benchmark Comparison}
\label{sec:benchmark}
Comparison of our system's performance against existing baselines and benchmarks.
