\chapter{Literature Review}
\phantomsection
\label{ch:literature}

\section{Overview of Optical Character Recognition (OCR)}
\phantomsection
\label{sec:ocr-overview}
This section provides a comprehensive overview of Optical Character Recognition technology, including its fundamental principles, key components, and evolution over time. The discussion covers both traditional and modern approaches to OCR, establishing the foundation for understanding current challenges and opportunities.

\section{Challenges in Khmer OCR}
\phantomsection
\label{sec:khmer-challenges}
This section examines the specific challenges faced in developing OCR systems for the Khmer script. Khmer writing presents unique structural complexities such as stacked characters and inconsistent spacing, making segmentation and recognition highly challenging \cite{muaz2015khmerocr}. It analyzes the unique characteristics of Khmer writing, including its complex character combinations, subscripts, and diacritics, which pose significant challenges for accurate recognition.

\section{Synthetic Data for Low-Resource Languages}
\phantomsection
\label{sec:synthetic-data}
The role of synthetic data generation in addressing the data scarcity problem for low-resource languages is explored here. This section reviews existing approaches to synthetic data creation and their effectiveness in training OCR systems.

\section{OCR Datasets and Benchmarks}
\phantomsection
\label{sec:datasets}
A comprehensive review of existing OCR datasets and evaluation benchmarks is presented, with particular focus on those relevant to Southeast Asian scripts and low-resource languages. The limitations of current datasets are also discussed.

\section{Deep Learning Models for Text Recognition}
\phantomsection
\label{sec:dl-models}

\subsection{CNN-based Methods}
\phantomsection
\label{subsec:cnn}
This subsection examines the application of Convolutional Neural Networks in OCR, including architectures specifically designed for text recognition tasks and their performance characteristics.

\subsection{Transformer-based Architectures}
\phantomsection
\label{subsec:transformer}
The emergence and impact of transformer-based models in OCR are analyzed, with particular attention to recent developments and their advantages over traditional approaches.

\section{Summary of Research Gaps}
\phantomsection
\label{sec:gaps}
This section synthesizes the key findings from the literature review and identifies critical gaps in current research, particularly in the context of Khmer OCR and low-resource language processing. These gaps form the basis for the research objectives addressed in this thesis.
