\chapter{Results and Analysis}
\phantomsection
\label{ch:results}

\section{Text Detection Results}
\label{sec:detection-results}

The text detection model, based on the CRAFT (Character Region Awareness for Text detection) 
architecture, was evaluated on a test set consisting of 20 images. The model achieved an impressive 
Intersection over Union (IoU) score of 0.98 when compared to the ground truth annotations, 
demonstrating high accuracy in detecting text regions.

The training process was conducted on a dataset of 175 images, with an additional 20 images 
used for validation. The evaluation results indicate that the model is capable of accurately 
detecting text in all test images, showcasing its generalization ability and robustness across 
various text-containing scenes.

\subsection{Accuracy on Character, Word, Sentence Levels}
\label{subsec:accuracy}
Detailed analysis of recognition accuracy at different granularities - character level, word level, and complete sentence level.

\subsection{Performance Across Sentence Lengths}
\label{subsec:performance}
Analysis of how recognition performance varies with different sentence lengths and complexity levels.

\section{Khmer vs. English Performance}
\label{sec:comparison-results}
Comparative analysis of the system's performance on Khmer text versus English text, highlighting key differences and challenges.

\section{Error Analysis and Failure Cases}
\label{sec:error-analysis}
Systematic analysis of common error patterns and challenging cases that lead to recognition failures.

\section{System Robustness and Generalization}
\label{sec:robustness}
Evaluation of the system's ability to generalize across different document types, fonts, and image quality conditions.
